### 2018-04-19 project.tex
Update
Sigma->Lindelof
Corrections

	\begin{theorem}
	$\lbrace\mathbb{X}\rbrace$ is a basis for $\tau$ = $\lbrace\emptyset$, $\mathbb{X}\rbrace$. (indiscrete)
	\end{theorem}
	\begin{proof}:\newline
	\begin{enumerate}
		\item Let $\mathcal{B} = \lbrace\mathbb{X}\rbrace$ and let $x \in \mathbb{X} = B \in \mathcal{B}$.
		\item Now consider $B_1, B_2 \in \mathcal{B}$. $B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 = \mathbb{X} : B_1 \cap B_2 = \mathbb{X}$.
		\item Choose $\mathcal{B}_\emptyset = \emptyset \subseteq \mathcal{B}$ and $\mathcal{B}_\mathbb{X} = \lbrace \mathbb{X} \rbrace \subseteq \mathcal{B}$ where $\bigcup \mathcal{B}_\emptyset = \emptyset$ and $\bigcup \mathcal{B}_\mathbb{X} = \mathbb{X}$, so since $\mathcal{P}(\mathcal{B}) = \lbrace \emptyset, \lbrace \mathbb{X} \rbrace \rbrace$, $\lbrace \bigcup \mathcal{B'} : \mathcal{B'} \subseteq \mathcal{B} \rbrace = \lbrace \bigcup \mathcal{B}_\emptyset, \bigcup \mathcal{B}_\mathbb{X} \rbrace = \tau = \lbrace \emptyset, \lbrace \mathbb{X} \rbrace \rbrace$.
	\end{enumerate}
	\end{proof}

	\begin{theorem}
	$\mathcal{B} = \lbrace\lbrace x \rbrace$ : x $\in \mathbb{X}\rbrace$ is a basis for $\tau$ = $\mathcal{P}(\mathbb{X})$ = $\lbrace$ U : U $\subseteq \mathbb{X} \rbrace$. (discrete)
	\end{theorem}
	\begin{proof}:\newline
		\begin{enumerate}
			\item Let $x \in U \in \tau = \mathcal{P}(\mathbb{X})$. Then for $B = \lbrace x \rbrace \in \mathcal{B}, x \in B \subseteq U$.
			\item Let $B_1, B_2 \in \mathcal{B}$. Let $y \in B_1 \cap B_2$. Let $B_3 = \lbrace y \rbrace$ $y \in B_3 = \lbrace y \rbrace \subseteq B_1 \cap B_2$. 
			\item Let $U \in \tau = \mathcal{P} \lbrace \mathbb{X} \rbrace$. Then $U = \lbrace x : x \in U \rbrace = \bigcup \lbrace x \rbrace = \bigcup \mathcal{B}_U$ for $\mathcal{B}_U = \lbrace \lbrace x \rbrace : x \in U \rbrace \subseteq \mathcal{B}$.
			\item Let $\mathcal{B'} \subseteq \mathcal{B}$. Then $\bigcup \mathcal{B'} \in \mathcal{P}(\mathbb{X}) \in \tau$.
		\end{enumerate}
	\end{proof}

@@

	\begin{proof}
	For $F = \lbrace x_i : 0 \leq i < n \rbrace \subseteq \mathbb{X}$, let $\mathcal{U}$ be an open covering of $F$ so $\bigcup \mathcal{U} \supseteq F$. For each $0 \leq i < n$, let $\mathcal{U}_i \in \mathcal{U}$ satisfy $x_i \in \mathcal{U}_i$. Let finite $\mathcal{F} = \lbrace U_i : 0 \leq i < n \rbrace \subseteq \mathcal{U}$, so $\bigcup \mathcal{F} \supseteq F$ and $F$ is compact.
	\end{proof}

@@

	\begin{proof}
	Let $K = \lbrace 0 \rbrace \cup \lbrace \frac{1}{n} : n \in \mathbb{Z^+} \rbrace \subseteq \mathbb{R}$ and let $\mathcal{U}$ be an open covering of $K$. We may choose $U_0 \in \mathcal{U}$ where $0 \in U_0$. So pick $a<b \in \mathbb{R}$ where $0 \in (a, b) \subseteq U_0$. Let $N \in \mathbb{Z}^+$ where $0 < \frac{1}{N} < b$. Now let finite $F = \lbrace \frac{1}{m} : 1 \leq m < N \rbrace$ so it is compact, and choose $\mathcal{F} \subseteq \mathcal{U}$ with $\bigcup \mathcal{F} \supseteq F$. So $K = \lbrace \frac{1}{n} : n \in \mathbb{Z}^+$ and $n \geq N \rbrace$. $\bigcup n \in \mathbb{Z}_+$ and $\lbrace \frac{1}{n} : 1 \leq n < N \rbrace$ is covered by $\lbrace U_0 \rbrace \cup \mathcal{F}$.
	\end{proof}

@@

	\begin{proposition}
	  Any open interval \((a,b)\subseteq\mathbb R\) is not compact.
	\end{proposition}
	\begin{proof}
	Let $K = (a, b) \subseteq \mathbb{R}$, Let $\mathcal{U} = \lbrace (x, y) : x, y \in \mathbb{R}, a \leq x < y \leq b \rbrace$. So, $\bigcup \mathcal{U} \supseteq K$, and $\bigcup \mathcal{U} = K$. Let $n \in \mathbb{Z}$, let $x_i, y_i \in \mathbb{R}$ be arbitrary with $0 \leq i < n$. Then, $\mathcal{F} = \lbrace (x_i, y_i) : 0 \leq i < n \rbrace$ is an arbitrary finite subset of $\mathcal{U}$. However $\mathcal{F} \not\supseteq K$, for $min(x_i : 0 \leq i < n)$ and $max(y_i : 0 \leq i < n)$ we can find a $k \in K : k < min(x_i : 0 \leq i < n)$ or $k > max(y_i : 0 \leq i < n)$ so $k \not\in \bigcup \mathcal{F}$ and $K$ is not compact.
	\end{proof}

@@

	\begin{definition}
	  A subset \(K\) of a topological space \(X\) is said to be \textbf{\(\sigma\)-compact} if
	  there exist compact subspaces \(K_n\) of \(X\) for \(n\in\mathbb N\) such that
	  \(K=\bigcup_{n\in\mathbb N} K_n\).
	\end{definition}

	\begin{theorem}
		Every \(\sigma\)-compact subset of a topological space is Lindel\"of.
	\end{theorem}
	\begin{proof}
	\end{proof}

>>>>

	\begin{theorem}
	$\lbrace\mathbb{X}\rbrace$ is a basis for $\tau$ = $\lbrace\emptyset$, $\mathbb{X}\rbrace$. (indiscrete)
	\end{theorem}
	\begin{proof}:\newline
	\begin{enumerate}
		\item Let $\mathcal{B} = \lbrace\mathbb{X}\rbrace$ and let $x \in \mathbb{X} = B \in \mathcal{B}$.
		\item Now consider $B_1, B_2 \in \mathcal{B}$. $B_1 = \mathbb{X}$ and $B_2 = \mathbb{X}$ Let $x \in B_1 \cap B_2$, then $x \in B_3 \subseteq B_1 \cap B_2$.
		\item Choose $\mathcal{B}_\emptyset = \emptyset \subseteq \mathcal{B}$ and $\mathcal{B}_\mathbb{X} = \lbrace \mathbb{X} \rbrace \subseteq \mathcal{B}$ where $\bigcup \mathcal{B}_\emptyset = \emptyset$ and $\bigcup \mathcal{B}_\mathbb{X} = \mathbb{X}$, so since $\mathcal{P}(\mathcal{B}) = \lbrace \emptyset, \lbrace \mathbb{X} \rbrace \rbrace$, $\lbrace \bigcup \mathcal{B'} : \mathcal{B'} \subseteq \mathcal{B} \rbrace = \lbrace \bigcup \mathcal{B}_\emptyset, \bigcup \mathcal{B}_\mathbb{X} \rbrace = \tau = \lbrace \emptyset, \lbrace \mathbb{X} \rbrace \rbrace$.
	\end{enumerate}
	\end{proof}

	\begin{theorem}
	$\mathcal{B} = \lbrace\lbrace x \rbrace$ : x $\in \mathbb{X}\rbrace$ is a basis for $\tau$ = $\mathcal{P}(\mathbb{X})$ = $\lbrace$ U : U $\subseteq \mathbb{X} \rbrace$. (discrete)
	\end{theorem}
	\begin{proof}:\newline
		\begin{enumerate}
			\item Let $x \in U \in \tau = \mathcal{P}(\mathbb{X})$. Then for $B = \lbrace x \rbrace \in \mathcal{B}, x \in B \subseteq U$.
			\item Let $B_1, B_2 \in \mathcal{B}$. Let $y \in B_1 \cap B_2$. Let $B_3 = \lbrace y \rbrace$ $y \in B_3 = \lbrace y \rbrace \subseteq B_1 \cap B_2$. 
			\item Let $U \in \tau = \mathcal{P} ( \mathbb{X} )$. Then $U = \lbrace x : x \in U \rbrace = \bigcup \lbrace x : x \in U \rbrace = \bigcup \mathcal{B}_U$ for $\mathcal{B}_U = \lbrace \lbrace x \rbrace : x \in U \rbrace \subseteq \mathcal{B}$.
			\newline Let $\mathcal{B'} \subseteq \mathcal{B}$. Then $\bigcup \mathcal{B'} \in \mathcal{P}(\mathbb{X}) \in \tau$.
		\end{enumerate}
	\end{proof}

@@

	\begin{proof}
	For $F = \lbrace x_i : 0 \leq i < n \rbrace \subseteq \mathbb{X}$, let $\mathcal{U}$ be an open covering of $F$ so $\bigcup \mathcal{U} \supseteq F$. For each $0 \leq i < n$, let $U_i \in \mathcal{U}$ satisfy $x_i \in U_i$. Let finite $\mathcal{F} = \lbrace U_i : 0 \leq i < n \rbrace \subseteq \mathcal{U}$, so $\bigcup \mathcal{F} \supseteq F$ and $F$ is compact.
	\end{proof}

@@

	\begin{proof}
	Let $K = \lbrace 0 \rbrace \cup \lbrace \frac{1}{n} : n \in \mathbb{Z^+} \rbrace \subseteq \mathbb{R}$ and let $\mathcal{U}$ be an open covering of $K$. We may choose $U_0 \in \mathcal{U}$ where $0 \in U_0$. So pick $a<b \in \mathbb{R}$ where $0 \in (a, b) \subseteq U_0$. Let $N \in \mathbb{Z}^+$ where $0 < \frac{1}{N} < b$. Now let finite $F = \lbrace \frac{1}{m} : 1 \leq m < N \rbrace$ so it is compact, and choose $\mathcal{F} \subseteq \mathcal{U}$ with $\bigcup \mathcal{F} \supseteq F$. So $K = \lbrace 0 \rbrace \cup \lbrace \frac{1}{m} : N \leq m < \infty \rbrace \cup \lbrace \frac{1}{m} : 1 \leq m < N \rbrace$.
	\end{proof}

@@

	\begin{proposition}
	  Any open interval \((a,b)\subseteq\mathbb R\) is not compact.
	\end{proposition}
	\begin{proof}
	Let $K = (a, b) \subseteq \mathbb{R}$, Let $\mathcal{U} = \lbrace (x, y) : x, y \in \mathbb{R}, a < x < y < b \rbrace$. So, $\bigcup \mathcal{U} \supseteq K$, and $\bigcup \mathcal{U} = K$. Let $n \in \mathbb{Z}$, let $x_i, y_i \in \mathbb{R}$ be arbitrary with $0 \leq i < n$. Then, $\mathcal{F} = \lbrace (x_i, y_i) : 0 \leq i < n \rbrace$ is an arbitrary finite subset of $\mathcal{U}$. However $\bigcup \mathcal{F} \not\supseteq K$, for $min(x_i : 0 \leq i < n)$ we can find a $k \in K : k < min(x_i : 0 \leq i < n)$ which is greater than $a$ so $k \not\in \bigcup \mathcal{F}$ and $K$ is not compact.
	\end{proof}

@@

	\begin{definition}
	  A subset \(K\) of a topological space \(X\) is said to be \textbf{\(\sigma\)-compact} if
	  there exist compact subspaces \(K_n\) of \(X\) for \(n\in\mathbb N\) such that
	  \(K=\bigcup_{n\in\mathbb N} K_n\).
	  \newline \newline
	\end{definition}
	\begin{theorem}
		Every \(\sigma\)-compact subset of a topological space is Lindel\"of.
	\end{theorem}
	\begin{proof}
	Let $K$ be \(\sigma\)-compact. Let $\mathcal{U}$ be an arbitrary collection of open sets such that $\bigcup \mathcal{U} \supseteq K$. Choose finite $\mathcal{F} = \lbrace F_i : i \in \mathbb{N} \rbrace \subseteq \mathcal{U}$ so $\mathcal{F}$ is countable. Let each $F_{i \in \mathbb{N}} \supseteq K_{n \in \mathbb{N}}$ so, $\bigcup \mathcal{F} = \bigcup_{i \in \mathbb{N}} F_i \supseteq \bigcup_{n \in \mathbb{N}} K_n = K$. Therefore $\bigcup \mathcal{F} \supseteq K$.

	\end{proof}
